Storing messages with multipartite neural cliques

### 2014-07-10 Articles/article.tex
résol bug bibtex

		a priori for noise on edges :

	$P(\mbox{no other vertex activated in this cluster})= \sum_{n = 1}^{a (c - c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] P(n_v < n)^{l-a}$%[ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$

	%P(\mbox{no other vertex activated in any cluster})
	\begin{align*}
	P_{retrieve}=  \Bigg ( \sum_{n = 1}^{a ( c- c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ]\\
	\left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \Bigg)^{c_e}	
	\end{align*}
	\newpage
	%$\,$
	%\newpage
	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/thpsi_c8l256e4}
		\caption{2 activities per cluster, 8 clusters, 256 neurons per cluster, 4 erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}
		\label{psith}
	\end{figure}

@@

	\nocite{*}
	\bibliographystyle{numeric} % Le style est mis entre crochets.
         \bibliography{bibli}
\end{document}

>>>>

	If $\gamma$ is big,
	$P(\mbox{no other vertex activated in this cluster})= \sum_{n = 1}^{a (c - c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ] P(n_v < n)^{l-a}$%[ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a }$

	%P(\mbox{no other vertex activated in any cluster})
	\begin{align*}
	P_{retrieve}=  \Bigg ( \sum_{n = 1}^{a ( c- c_e)} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{v_c} = n)^k P(n_{v_c} > n)^{a-k} \right ]\\
	\left [ \sum_{x = 0}^{n - 1} P(n_v = x) \right]^{l-a } \Bigg)^{c_e}	
	\end{align*}
	\newpage
	%$\,$
	%\newpage
	\begin{figure}[!htb]
		\includegraphics[width=8.5cm]{Courbes/thpsi_c8l256e4}
		\caption{$\psi = 0.05$, 2 activities per cluster, 8 clusters, 256 neurons per cluster, 4 erasures, each point is the mean of 10 networks with 1000 sampled messages, analytical result in continuous black}
		\label{psith}
	\end{figure}

@@

	\nocite{*}
	\bibliographystyle{plain} % Le style est mis entre crochets.
         \bibliography{bibli.bib}{}
\end{document}
